---
title: "Ski Pass Exploratory"
author: "Winston Saunders"
date: "March 26, 2015"
output: 
   html_document:
        toc: true
        toc_depth: 3
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=6, fig.height=3, fig.align='center', fig.path='Figs/', echo=FALSE, warning=FALSE, message=FALSE)
```


```{r}
        ## PASS NUMBER
        Pass <- "MBA6360970"

        Directory <- "/Users/winstonsaunders/Documents/Ski_Data2/"
        
        ski_runs<-read.csv(paste0(Directory,Pass,".csv"))

        Pass_Code<-"MBXXXXXXXX"

```

##Download Data from Pass `r Pass_Code`

Data are extracted from the [Track Your Turns](http://track.mtbachelor.com/index.asp) website at [Mt. Bachelor](http://www.mtbachelor.com/site). For this particular pass there are `r dim(ski_runs)[1]` total runs. 

Let's look at a sample of the ski runs data:

```{r, echo=TRUE}
print_sample<-sort(sample(1:dim(ski_runs)[1], 10))
print(ski_runs[print_sample,2:8])
```

From this data add a few extra columns of data as a start of features such as weekday, weekend, and holiday indicators to increase the feature set available for plotting. 

```{r}
library(timeDate)
library(chron)

ski_runs$weekend<-isWeekend(ski_runs$date)
ski_runs$holiday<-isHoliday(as.timeDate(ski_runs$date), holidays = holidayNYSE(), wday = 1:5)
ski_runs$bizday<-isBizday(as.timeDate(ski_runs$date))
```


##Daily vertical

We can slice and dice the data many ways. For this exploratory part we'll look at a couple of them just to get "dirty" with the data.  
One way, as below, is to sum vertical feet of runs to get total vertical feet skied per day.  

```{r "compute daily vert", echo=2}
## calculate daily vertical sums
daily_vert<-rowsum(ski_runs$vertical_feet, ski_runs$date)
daily_vert<-as.data.frame(daily_vert)
daily_vert$date<-rownames(daily_vert)


daily_vert <- transform(daily_vert,
                        week = as.POSIXlt(date)$yday %/% 7 + 1,
                        season_week = (as.POSIXlt(date)$yday+31)%%365 %/% 7+1,
                        wday = as.POSIXlt(date)$wday,
                        year = as.POSIXlt(date)$year+1900)

colnames(daily_vert)<-c("total_vertical","date","week","season_week" ,"wday","year")
```

Plotted as below, shows the daily total vert plotted as a function of "Ski Season Week" (i.e. weeks since Nov 1). The one point at week 40 is a high snow year, when they area opened on July 4th. 


```{r}
library(ggplot2)
p<-ggplot(daily_vert, aes(x=season_week, y= total_vertical)) + 
  geom_point(size=3)+ggtitle("Ski-Day Total Vertical")
print(p)
```
Another way to look at the data is as a histogram of daily total vertical for all ski days. 
```{r}
library(ggplot2)
p<-ggplot(daily_vert, aes(x= total_vertical)) + 
  geom_histogram(colour = "darkgreen", fill = "khaki4", binwidth = 2000, aes(y=..count..))
p <- p + ggtitle("Histogram of Daily Vertical Totals")
  
print(p)

```

```{r "get rid of scientific notation"}
options(scipen=999)
```

The mean vertical is `r round(mean(daily_vert$total_vertical),0)` feet over `r dim(daily_vert)[1]` days. The most frequent daily total is about 22000 feet / day.

##Visual Summary of Ski Seasons for `r Pass_Code`

This is an interesting way to look at individual ski days. Vertical feet for the day are encoded in color, with red representing the highest dailty vert. 

```{r, fig.align='center', fig.height=9, fig.width=6}
library(ggplot2)
p1<-ggplot(daily_vert, aes(week, wday, fill = total_vertical)) + 
  geom_tile(colour = "white") +
  scale_fill_gradientn(colours = c("khaki2", "darkgreen", "red")) + 
  facet_wrap(~ year, ncol = 1)

print(p1)
```

####Chair lift totals

Here we begin to look at the data in somewhat finer detail. For instance we can look at the total vertical feet skied on a particular chairlift per ski day.  

For the Pine Marten chair lift.  


```{r "compute daily Pine vert", echo=2}
## calculate daily vertical sums
Pine_runs <- ski_runs[ski_runs$chair=="Pine Marten",]
daily_vert<-rowsum(Pine_runs$vertical_feet, Pine_runs$date)
daily_vert<-as.data.frame(daily_vert)
daily_vert$date<-rownames(daily_vert)


daily_vert <- transform(daily_vert,
                        week = as.POSIXlt(date)$yday %/% 7 + 1,
                        season_week = (as.POSIXlt(date)$yday+31)%%365 %/% 7+1,
                        wday = as.POSIXlt(date)$wday,
                        year = as.POSIXlt(date)$year+1900)

colnames(daily_vert)<-c("total_vertical","date","week","season_week" ,"wday","year")
```


```{r, fig.height=8}
library(ggplot2)
p<-ggplot(daily_vert, aes(x=week, y= total_vertical, color=factor(wday))) + 
  geom_point(size=3) + ggtitle("Pine Marten") +facet_grid(year~.)
  
print(p)
```


```{r "compute daily Sunrise vert", echo=2}
## calculate daily vertical sums
Sunrise_runs <- ski_runs[ski_runs$chair=="Sunrise",]
daily_vert<-rowsum(Sunrise_runs$vertical_feet, Sunrise_runs$date)
daily_vert<-as.data.frame(daily_vert)
daily_vert$date<-rownames(daily_vert)


daily_vert <- transform(daily_vert,
                        week = as.POSIXlt(date)$yday %/% 7 + 1,
                        season_week = (as.POSIXlt(date)$yday+61)%%365 %/% 7+1,
                        wday = as.POSIXlt(date)$wday,
                        year = as.POSIXlt(date)$year+1900)

daily_vert$count<-1:dim(daily_vert)[1]

colnames(daily_vert)<-c("total_vertical","date","week","season_week" ,"wday","year", "count")
```

```{r, fig.height=8}
library(ggplot2)
p<-ggplot(daily_vert, aes(x=week, y= total_vertical, color=factor(wday))) + 
  geom_point(size=3) + ggtitle("Sunrise")+facet_grid(year~.)
  
print(p)
```

And as a last version, let's just look at all of the sunrise totals. But rather than look at just the numbers, let's look at the z-statistic for totals to look for outliers. Now this is starting to look likesomething useful...

```{r}
head(daily_vert)
```

```{r, "sunrise", fig.height=4, fig.width=8}
library(ggplot2)

mean_vert<-mean(daily_vert$total_vertical)
sdev_vert<-sqrt(var(daily_vert$total_vertical))


daily_vert$z<-(daily_vert$total_vertical-mean_vert)/sdev_vert

p<-ggplot(daily_vert, aes(x=count, y=z, color=factor(wday))) + 
  geom_point(size=3) + ggtitle("Sunrise")+theme_bw()
  
print(p)
```

We can see, however, that the distribution has a very long tail....

```{r}
hist(daily_vert$z)

```


###Chairlift Usage

We can look if there are patterns in the charilift usage by looking for trends and patterns in the data on which chairs are ridden...

####Chairlift Frequency

First, let's just look at the number of rides on all chairs

```{r, fig.height=5}

chair_table<-table(ski_runs$chair)

barplot(sort(chair_table, decreasing=TRUE), cex.names=.9, las=2)
```

We can use this to test each day against this pattern...

```{r}

chair_list <- unique(ski_runs$chair)

date_list<-unique(ski_runs$date)

date_list_length<-length(date_list)

run_list<-NULL
for (i in 1:date_list_length) {
        
        a <-table(ski_runs$chair[ski_runs$date==date_list[i]])
        a<-as.data.frame(a)
     
        char_date<-as.character(as.Date(date_list[i]))
        
        ski_date<-rep(char_date, dim(a)[1])
     
        a<-cbind(a, ski_date)
 
        run_list<-rbind(run_list,a)
 
}

```

```{r}
head(run_list)

```

###Visualizing Chair Rides Per Day
Let's explore graphically how frequently chairlifts are used throughout the season. 


```{r "try a season hack"}



season_hacker<-function(x)
        {
        d<-as.Date(x)
        
        ## brute force seasons
        if (d<as.Date("2015-08-01")){b<-"14-15"
                } 
        if (d<as.Date("2014-08-01")){b<-"13-14"
                }
        if (d<as.Date("2013-08-01")){b<-"12-13"
                }
        if (d<as.Date("2012-08-01")){b<-"11-12"
                }
        if (d<as.Date("2011-08-01")){b<-"10-11"
                }
        if (d<as.Date("2010-08-01")){b<-"09-10"
                }
        if (d<as.Date("2009-08-01")){b<-"08-09"
                }
        if (d<as.Date("2008-08-01")){b<-"07-08"
                }
        if (d<as.Date("2007-08-01")){b<-"06-07"
                }
        if (d<as.Date("2006-08-01")){b<-"05-06"
                }
        return(b)
        }

```

```{r}

date_list<-as.character(run_list$ski_date)

season<-lapply(date_list, season_hacker)

season <- as.character(season)

run_list <- cbind(run_list, season)

## add some more features
run_list <- transform(run_list,
                week = as.POSIXlt(ski_date)$yday %/% 7 + 1,
                season_day = (as.POSIXlt(ski_date)$yday+61)%%365+1,
                wday = as.POSIXlt(ski_date)$wday,
                year = as.POSIXlt(ski_date)$year+1900)


```

```{r, fig.width=10, fig.height=6}
library(ggplot2)
p<-ggplot(run_list[run_list$Freq>0,], aes(x=season_day, y=Var1, size=Freq, color=factor(wday)))
p<-p + geom_point()
p <- p + facet_wrap(~season, ncol=2)
p<-p + theme(axis.text.x=element_text(angle=60, size=10, vjust=0.5), 
             axis.text.y=element_text(size=8))
p <- p + ggtitle("chair counts for all seasons")
print(p)

```

Let's zoom in on a couple of seasons

```{r, fig.width=8, fig.height=3}
library(ggplot2)
p<-ggplot(run_list[run_list$Freq>0 & run_list$season=="08-09",], aes(x=season_day, y=Var1, size=Freq, color=factor(wday)))
p<-p + geom_point()
p<-p + theme(axis.text.x=element_text(angle=60, size=10, vjust=0.5), 
             axis.text.y=element_text(size=12))
p<-p + ggtitle("chair counts for season 08-09")
print(p)

```

```{r, fig.width=8, fig.height=3}
library(ggplot2)
p<-ggplot(run_list[run_list$Freq>0 & run_list$season=="11-12",], aes(x=season_day, y=Var1, size=Freq, color=factor(wday)))
p<-p + geom_point()
p<-p + theme(axis.text.x=element_text(angle=60, size=10, vjust=0.5), 
             axis.text.y=element_text(size=12))
p<-p + ggtitle("chair counts for season 11-12")
print(p)

```
